\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[sfdefault]{roboto}

\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedright
\raggedbottom
\setlength{\tabcolsep}{0in}

% Section formatting (tight)
\titleformat{\section}{\Large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{3pt}{3pt}

% Custom commands (COMPACT)
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%––––– HEADER –––––
\begin{center}
  {\Huge \textbf{Shival Gupta}} \\
  \vspace{6pt}
  \small
  +91 7091041542 $|$
  \href{mailto:sgupta.5545@gmail.com}{sgupta.5545@gmail.com} $|$
  \href{https://github.com/shival-gupta}{github.com/shival-gupta} $|$
  \href{https://linkedin.com/in/shival-gupta}{linkedin.com/in/shival-gupta} $|$
  \href{https://shivalgupta.me}{shivalgupta.me}
\end{center}

%––––– SUMMARY –––––
\section{Professional Summary}
\resumeSubHeadingList
\vspace{2pt}
  \resumeItem{CS Graduate specializing in Web, XR, and AI, with hands-on experience building defense simulations, autonomous robots, and agent-driven smart home systems.}
\resumeSubHeadingListEnd

%––––– SKILLS –––––
\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Languages}: Java, Python, C, C++, C\#, SQL}
  \vspace{-4pt}
  \resumeItem{\textbf{Web}: Next.js, Tailwind CSS, Clerk.js, Prisma ORM, PostgreSQL, WebSockets}
  \vspace{-4pt}
  \resumeItem{\textbf{AI \& Robotics}: ROS, Jetson Nano, Arduino, RAG pipelines, multi-agent systems}
  \vspace{-4pt}
  \resumeItem{\textbf{Tools}: Git, Docker, Unity, Blender, OpenXR (VR)}
\resumeSubHeadingListEnd

%––––– PROJECTS –––––
\vspace{-8pt}
\section{Projects}
\resumeSubHeadingList
\vspace{2pt}
  \resumeSubheading
    {Autonomous Omni-Wheel Library Robot (Capstone)}{Jan 2025 -- Apr 2025}
    {Jetson Nano, ROS, Arduino, Python, C++, Docker}
    {\href{https://shivalgupta.me/projects/}{[Video]}}
    \resumeSubHeadingList
      \resumeItem{Integrated Jetson Nano with Arduino for real-time motor control and AI-based navigation.}
      \resumeItem{Implemented ROS-based LiDAR mapping and IR-guided line following for indoor autonomy.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {Smart Home Automation (Samsung PRISM Worklet)}{Sep 2024 -- Jun 2025}
    {Unity, crewAI, WebSockets, Next.js}
    {\href{https://projects.shivalgupta.me/SmartHome-AgenticAI-Simulation/}{[Live Demo]}}
    \resumeSubHeadingList
      \resumeItem{Built a 3D smart home simulation in Unity as a testbed for autonomous AI agents.}
      \resumeItem{Connected AI backend with real-time device orchestration using WebSocket and HTTP.}
      \resumeItem{Developed a control dashboard for monitoring and agent-based interactions.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {Samsung Store XR (PRISM Challenge Winner)}{Feb 2024 -- Jul 2024}
    {Unity, OpenXR, Blender}
    {\href{https://shivalgupta.me/projects/}{[Demo Video]}}
    \resumeSubHeadingList
      \resumeItem{Developed a VR prototype of Samsung’s retail store for Meta Quest and other XR devices.}
      \resumeItem{Implemented teleportation, interactive product showcases, and virtual cart systems.}
    \resumeSubHeadingListEnd

\resumeSubHeadingListEnd

%––––– EXPERIENCE –––––
\section{Experience}
\resumeSubHeadingList
\vspace{2pt}
  \resumeSubheading
    {Systems Engineer (ILP Trainee)}{Jan 2026 -- Present}
    {Tata Consultancy Services (TCS)}{}
    \vspace{2pt}

  \resumeSubheading
    {XR Developer Intern}{Feb 2025 -- Jun 2025}
    {SatoriXR, Chennai, India}{\href{https://drive.google.com/file/d/1bNjF0U-Ky607ieK9sgrpSHBlJc7LPmNN/view}{Certificate}}
    \resumeSubHeadingList
      \resumeItem{Led a cross-functional team of developers and 3D artist on a defense-focused VR simulation.}
      \resumeItem{Processed DEMs and satellite imagery into interactive Unity-based terrain systems.}
      \resumeItem{Implemented missile trajectory modeling and Google Earth-style visualization tools.}
      \resumeItem{Assisted in hosting OpenProject (open-source Jira alternative) on Azure using Docker.}
    \resumeSubHeadingListEnd

  \resumeSubheading
    {Software Developer Intern}{Sep 2023 -- Nov 2023}
    {Airtel Payments Bank, New Delhi}{\href{https://drive.google.com/file/d/1zCj8CKZbHcKEj6LS8N3VzG33aIENUIZA/view}{Certificate}}
    \resumeSubHeadingList
      \resumeItem{Worked in Agile/Scrum workflows for fintech application development.}
      \resumeItem{Built a secure full-stack B2B SaaS prototype for enterprise transactions.}
      \resumeItem{Implemented Next.js, Prisma, and PostgreSQL with encryption and RBAC.}
      \resumeItem{Integrated third-party authentication and modern UI using Tailwind and shadcn.}
    \resumeSubHeadingListEnd

\resumeSubHeadingListEnd

%––––– EDUCATION –––––
\section{Education}
\resumeSubHeadingList
  \resumeSubheading
    {B.Tech in Computer Science and Engineering (AI \& Robotics)}{2021 -- 2025}
    {Vellore Institute of Technology, Chennai}{CGPA: 7.84}
  \resumeSubheading
    {Senior Secondary (CBSE XII)}{2020}
    {St. Karen's High School, Patna}{62.17\%}
  \resumeSubheading
    {Secondary (CBSE X)}{2018}
    {St. Karen's High School, Patna}{75.67\%}
\resumeSubHeadingListEnd

%––––– EXTRACURRICULAR –––––
\section{Extracurricular Activities}
\resumeSubHeadingList
  \resumeItem{Piano, Skating, Badminton, Photography, Videography}
\resumeSubHeadingListEnd

\end{document}