%-------------------------
% Shival Gupta Resume
% Author: Shival Gupta
% License : MIT
%------------------------

\documentclass[a4paper,10pt]{article}

% Layout and margins
\usepackage[margin=0.6in]{geometry} 

% Essential packages
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}

% Font selection 
\usepackage{fontspec}
\setmainfont{Roboto} 

% Color definitions
\definecolor{accentcolor}{HTML}{007bff}

% Styling adjustments
\usepackage{titlesec}
\titleformat{\section}{\Large\bfseries}{}{0em}{} 
\titlespacing*{\section}{0pt}{10pt}{4pt}

% Custom commands for consistent spacing
\newcommand{\sectionbreak}{\vspace{0.2em}} % Space between sections
\newcommand{\subsectionbreak}{\vspace{0em}} % Space between subsections

% Remove page numbers
\pagestyle{empty} 

\begin{document}

% Header
\begin{center}
    \centering
    {\fontsize{24pt}{28pt}\selectfont \textbf{Shival Gupta}} \\
    \vspace{0.2cm}
    \small Chennai, India | +91 7091041542 | \href{mailto:sgupta.5545@gmail.com}{\textcolor{accentcolor}{sgupta.5545@gmail.com}} \\
    \href{https://shivalgupta.tech/}{\textcolor{accentcolor}{shivalgupta.tech}} | \href{https://github.com/shival-gupta/}{\textcolor{accentcolor}{github.com/shival-gupta}} | \href{https://linkedin.com/in/shival-gupta/}{\textcolor{accentcolor}{linkedin.com/in/shival-gupta}}
\end{center}

\vspace{-0.3cm}

% Horizontal rule before Summary
\noindent \hrulefill

% \sectionbreak

% Objective Section 
\section{Summary}
Seeking a challenging role in AI, Robotics, and 3D development where I can leverage my skills, expertise, and passion for innovation to contribute to organizational success and create immersive experiences.

\sectionbreak

% Education Section (Tabular format)
\section{Education}

\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Degree/Program} & \textbf{Institution} & \textbf{Year} & \textbf{CGPA/Percentage} \\ \hline
B.Tech, Computer Science \& Engineering & Vellore Institute of Technology, Chennai & 2021 - 2025 & 7.82 \\ \hline
Senior Secondary (XII), Science (PCM) & St. Karen's High School, Patna (CBSE) & 2020 & 62.167\% \\ \hline
Secondary (X) & St. Karen's High School, Patna (CBSE) & 2018 & 75.67\% \\ \hline
\end{tabular}

\sectionbreak

% Skills Section 
\section{Skills}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \textbf{Programming Languages:} C, C++, C\#, Python, Java and TypeScript.
    \item \textbf{Frameworks \& Tools:} Next.js, Prisma, Tailwind, MySQL, PostgreSQL.
    % \item \textbf{AI \& ML:} Machine Learning, Deep Learning, Computer Vision, Numpy, Panda, Scikit-Learn.
    \item \textbf{IoT \& Robotics:} Arduino, Raspberry Pi, ROS, MQTT, and ThingSpeak.
    \item \textbf{3D \& Game Development:} Blender, Unity Engine, Unreal Engine, and After Effects.
\end{itemize}
\sectionbreak

% Experience Section 
\section{Experience}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \href{https://drive.google.com/file/d/1zCj8CKZbHcKEj6LS8N3VzG33aIENUIZA/view?usp=sharing}{\textcolor{accentcolor}{\textbf{
Software Development Intern, Airtel Payments Bank}}} | Sep 2023 - Nov 2023
        \subsectionbreak
        \begin{itemize}
            \item Collaborated across teams to deliver new features on schedule and with high quality.
            \item Conducted comprehensive software testing and debugging to ensure optimal performance.
        \end{itemize}
        \subsectionbreak
\end{itemize}

\sectionbreak

% Projects Section 
\section{Projects}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \href{https://github.com/Shival-Gupta/SamsungStoreXR}{\textcolor{accentcolor}{\textbf{SamsungStoreXR:}}} Developed a virtual reality app compatible with Oculus Meta Quest, HTC, and other VR headsets, leveraging Unity, Blender, and the OpenXR Toolkit for the Samsung Prism Metaverse Internship.
    \item \href{https://b2b-portal-rho.vercel.app/}{\textcolor{accentcolor}{\textbf{B2B Platform:}}} Developed a B2B solution using Next.js, Tailwind CSS, Prisma ORM, PostgreSQL, and Next-Auth for Airtel Payments Bank.
    \item \href{https://github.com/Shival-Gupta/obstacle-avoidance-car-ros-noetic}{\textcolor{accentcolor}{\textbf{Obstacle Avoidance Car:}}} Implemented an Obstacle Avoidance Car using ROS, Arduino, ultrasonic sensors, DC motors, and a motor driver.
    \item \href{https://github.com/Shival-Gupta/VoiceAI}{\textcolor{accentcolor}{\textbf{Voice AI:}}} Created a Python-based voice assistant inspired by Google Voice Assistant.
    \item \href{https://github.com/Shival-Gupta/WarGame}{\textcolor{accentcolor}{\textbf{3D Multiplayer Game:}}} Designed a 3D multiplayer First Person Shooter (FPS) game inspired by CS:GO, using Unity Engine and Photon Network.
    \item \href{https://github.com/Shival-Gupta/QuizApp}{\textcolor{accentcolor}{\textbf{Quiz App:}}} Built a Java and MySQL-based quiz application with login, leaderboard, and timer features.
\end{itemize}


\sectionbreak

% Achievements Section 
\section{Achievements}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \href{https://drive.google.com/file/d/19xeCrN3ycqXisyDDgIYeygRRVawMKOxu/view?usp=sharing}{\textcolor{accentcolor}{\textbf{Winner}, Samsung PRISM Metaverse Challenge}}
    \item Ranked 17th among 500 entries in a college-level CTF event "PASSWORD" organized by Linux Club VITC.
\end{itemize}

% Positions of Responsibility Section 
\section{Positions of Responsibility}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \textbf{Technical Lead (Game Development Club), VIT Chennai}
        \subsectionbreak
        \begin{itemize}
            \item Conducted workshops and organized events, overseeing game development activities.
            \item Played a pivotal role in fostering technical skills and creativity within the club.
        \end{itemize}
        \subsectionbreak
\end{itemize}

\sectionbreak

% Extracurricular Activities Section 
\section{Extracurricular Activities}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Piano, Skating, Badminton, Photography, Videography, Video Editing, 3D Animation
\end{itemize}

\sectionbreak


\end{document}